preciseTAD: A machine learning framework for precise TAD boundary prediction at base level resolution

### 2020-08-17 Manuscript/manuscript.Rmd
Polish legend for Supplementary Table 4

**Supplementary Table 4.** *preciseTAD* predicted boundary regions (PTBR) and points (PTBP) for GM12878 and K562, using Arrowhead TAD and Peakachu chromatin loop boundary coordinates as ground truth. For PTBRs, the start and end coordinates define the clusters of spatially proximate bases with probabilities equal to 1. For PTBPs, the start and end (start+1) coordinates define the uniquely identified boundary coordinate predicted by *preciseTAD* within each PTBR.

>>>>

**Supplementary Table 4.** *preciseTAD* predicted boundary regions (PTBR) and points (PTBP) for GM12878 and K562, using Arrowhead TAD and Peakachu chromatin loop boundary coordinates as ground truth. For PTBRs, the start and end coordinates define the clusters of spatially proximal bases with the probability of being a boundary equal to 1. For PTBPs, the start and end (start+1) coordinates define the uniquely identified boundary coordinate within each PTBR. All coordinates are in hg18/GRCh37 reference genome.
